Figures

### 2018-10-31 manuscript/figures.Rmd
towards an nlcd versus cdl comparison
add figure legend
towards systematic census data pull

>>>>

```{r nlcd-versus-cdl, fig.cap = "Comparison between NLCD derived and CDL derived total watershed ag and watershed pasture cover.", warning=FALSE, echo = FALSE}
knitr::include_graphics("../figures/04_nlcd-versus-cdl-1.pdf")
```

```{r cafos, fig.cap = "CAFOS", warning=FALSE, echo = FALSE}
knitr::include_graphics("../figures/05_cafos-1.pdf")
```
